---
title: "Alfa de Cronbach Policorica"
output: html_Alfa de Cronbach Policorica
---


Para correr una linea, utilizar *Ctrl+Shift+Enter*

Para insertar una nueva linea de codigo, utilizar *Ctrl+Alt+I*

```{r}
##Iniciar función paquetes
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
```


```{r}
##Asignar paquetes
packages <- c("parameters","apa","haven","ggplot2","ggpubr","gridExtra","apaTables", "reshape", "GPArotation", "mvtnorm", "psych", "psychometric", "lavaan", "nFactors", "semPlot", "lavaan", "MVN", "semTools")

```


```{r}
##Abrir paquetes
ipak(packages)
```


```{r}
##Abrir archivo de trabajo
Estructura11
```


```{r}
##Limpiar base de datos
DatosL <- na.omit(Estructura11)
```


```{r}
##Abrir base limpia
DatosL
```


```{r}
### Crea una subdata de cada factor
subdatos_Factor1 <- data.frame(cbind(DatosL$Q17_2, DatosL$Q17_3, DatosL$Q17_4, DatosL$Q17_1, DatosL$Q17_9, DatosL$Q17_7))

```


```{r}
### Genera una matriz poligorica, utilizada cuando se tienen variables ordinales
Poly_Factor1 <- polychoric(subdatos_Factor1)
```


```{r}
### Obten el Alfa ordinal
psych::alpha(Poly_Factor1$rho) ##escribirlo en la consola, sino no saldrá
```

```{r}
### Informa los descriptivos
describe(subdatos_Factor1)
```


```{r}
#Guardar la syntaxis del trabajo

```


Guardar la syntaxis del trabajo
Utilizar *Ctrl+Shift+K* sobre un Chunk (linea de trabajo)


```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
